---
title: "Changes in Ho Chi Minh city map"
---

## Summary

Changes in administrative levels in HCM city from 2000 - 2026

- **2003** - 2 new districts and reorganize communes ([ref](https://thuvienphapluat.vn/van-ban/Bo-may-hanh-chinh/Nghi-dinh-130-2003-ND-CP-lap-quan-BinhTan-Phu-phuong-truc-thuoc-dieu-chinh-dia-gioi-hanh-chinh-phuong-thuoc-quan-xa-thi-tran-Binh-Chanh-Can-Gio-51572.aspx))

  - Tan Phu (split from Tan Binh)

  - Binh Tan (split from Binh Chanh)

- **2006** - Reorganize communes in 3 districts ([ref](https://chinhphu.vn/default.aspx?pageid=27160&docid=17997))

  - Adjust communes in 3 districts: Go Vap, District 12, Tan Binh

- **2021** - Establish Thu Duc city and **more** commune adjustments ([ref](https://www.quanlynhanuoc.vn/2020/12/31/nghi-quyet-so-1111-nq-ubtvqh14-ve-viec-sap-xep-don-vi-hanh-chinh-cap-huyen-cap-xa-va-thanh-lap-tp-thu-duc-thuoc-tp-hcm/#:~:text=C%E1%BB%A5%20th%E1%BB%83%2C%20th%C3%A0nh%20l%E1%BA%ADp%20TP,s%E1%BB%91%20h%C6%A1n%201%20tri%E1%BB%87u%20ng%C6%B0%E1%BB%9Di.))

  - Thu Duc city merged from 3 districts: 2, 9 and Thu Duc

  - Adjust communes under Thu Duc city

- **2023** - Reorganize communes (again) ([ref](https://luatvietnam.vn/tin-van-ban-moi/sap-xep-dvhc-cap-xa-10-quan-cua-tp-hcm-giai-doan-2023-2025-186-100018-article.html))

  - Adjust communes in several districts: 3,4,5,6,8,10, 11,Phu Nhuan, Binh Thanh, Go Vap
`
- **2025** - Expand city and remove district level ([ref](https://thuvienphapluat.vn/phap-luat/ho-tro-phap-luat/tra-cuu-168-phuong-xa-tphcm-chinh-thuc-sau-sap-nhap-nam-2025-day-du-chi-tiet-danh-sach-toan-bo-phuo-570655-223893.html))

  - Merge Binh Duong and Vung Tau to Ho Chi Minh city

  - Remove districts level, merge existing communes into 168 communes

Overview

- **2000 - 2003:** 22 districts, 317 communes

- **2003 - 2021:** 24 districts, 322 communes

- **2021 - 2023:** 22 districts, 312 communes

- **2023 - 2025:** 22 districts, 273 communes

- **2025 - present (April, 2026):** 168 communes

## Data for R

### Preparing data

Since not all changes are captured on open-sourced shapefile data, we can use available datasets for major changes and manually merge polygons for minor ones.

Source for raw data

- **Before 2021 reform**: GADM 4.1 (24 districts, 322 communes)

- **After 2025 reform:** GIS VN (168 communes)

```{r warning=FALSE, message=FALSE}
# Load some dependencies
library(tidyverse)
library(sf)
library(terra)
library(janitor)
library(stringi)
library(downloadthis)
```

```{r warning=FALSE, message=FALSE}
#| code-fold: true
#| code-summary: "Preparing district data"
# Roughly HCMC spatial extent
cropvector <- c(106.2, 107.2, 10.2, 11.3)
# hcmc_extent <- ext(cropvector)

district_24 <- read_sf(
  "data/raw/before_reforms/gadm41_VNM_shp/gadm41_VNM_2.shp",
  options = "ENCODING=UTF-8"
) %>%
  clean_names() %>%
  st_crop(
    xmin = cropvector[1],
    xmax = cropvector[2],
    ymin = cropvector[3],
    ymax = cropvector[4]
  ) %>%
  filter(gid_1 == "VNM.25_1")
```

```{r warning=FALSE, message=FALSE}
#| code-fold: true
#| code-summary: "Preparing commune data"
commune_322 <- read_sf(
  "data/raw/before_reforms/gadm41_VNM_shp/gadm41_VNM_3.shp",
  options = "ENCODING=UTF-8"
) %>%
  clean_names() %>%
  st_crop(
    xmin = cropvector[1],
    xmax = cropvector[2],
    ymin = cropvector[3],
    ymax = cropvector[4]
  ) %>%
  filter(gid_1 == "VNM.25_1")

# The 168 communes map
commune_168 <- read_sf(
  "data/raw/after_2025_reforms/Việt Nam (phường xã) - 34/",
  options = "ENCODING=UTF-8"
) %>%
  filter(ten_tinh == "TP. Hồ Chí Minh")

commune_168 <- commune_168 %>%
  rename(
    name_1 = ten_tinh,
    id_1 = ma_tinh,
    name_2 = ten_xa,
    id_2 = ma_xa,
    type_2 = loai,
    merged_fr = sap_nhap
  ) %>%
  mutate(
    # make it a bit more consistent
    name_1 = str_remove(name_1, "TP. "),
    varname_2 = stri_trans_general(name_2, id = "Latin-ASCII")
  ) %>%
  select(
    name_1,
    id_1,
    name_2,
    id_2,
    varname_2,
    type_2,
    merged_fr,
    geometry
  )

# also 168 communes map but only mainland communes (no Con Dao island)
commune_167_mainland <- commune_168 %>%
  mutate(min_y = map(geometry, \(geom) st_bbox(geom)$ymin) %>% unlist()) %>%
  filter(min_y > 9) %>%
  select(-min_y)
```

```{r warning=FALSE, message=FALSE}
#| code-fold: true
#| code-summary: "Merge function"
# merge function
merge_poly_fn <- function(
  sf_dat,
  merge_map = list(
    "Thu Duc" = c("District 2", "District 9", "Thu Duc")
  ),
  colname = "varname_2"
) {
  walk(names(merge_map), \(new_shp) {
    old_shps <- merge_map[[new_shp]]

    merged <- sf_dat %>%
      filter(.data[[colname]] %in% old_shps) %>%
      st_union()

    if (new_shp %in% sf_dat[[colname]]) {
      # new_shp already exists --> update its geometry and drop other old shapes
      rm_shapes <- setdiff(old_shps, new_shp)
      sf_dat <<- sf_dat %>%
        mutate(
          geometry = if_else(.data[[colname]] == new_shp, merged, geometry)
        ) %>%
        filter(!(.data[[colname]] %in% rm_shapes))
    } else {
      # new_shp doesn't exist --> append new row and drop old shapes
      new_row <- tibble("{colname}" := new_shp, geometry = merged) %>% st_sf()
      sf_dat <<- sf_dat %>%
        filter(!(.data[[colname]] %in% old_shps)) %>%
        bind_rows(new_row)
    }
  })

  sf_dat
}
```

```{r}
#| code-fold: true
#| code-summary: "Data for download"
hcmc_shapefile <- list(
  boundary_pre_reform = district_24 %>% summarize(),
  boundary_post_reform = commune_168 %>% summarize(),
  district_24 = district_24, # sf
  commune_322 = commune_322, # sf
  commune_168 = commune_168, # sf
  commune_167_mainland = commune_167_mainland, # sf
  merge_poly_fn = merge_poly_fn # function to merge polygons
)
```

### Download data

Data for download is an R list with the following items

- `boundary_pre_reform` - HCM city boundary **before** merging with Vung Tau, Binh Duong

- `boundary_post_reform` - HCM city boundary **after** merging with Vung Tau, Binh Duong

- `district_24` - 24 districts in HCM city (during 2003 - 2021)

- `commune_322` - 322 communes in HCM city

- `commune_168` - 168 communes in HCM city (after 2025 reform)

- `commune_167_mainland` - Same as `commune_168` but only mainland communes (no Con Dao island)

```{r echo=FALSE}
# Download data
download_this(
  hcmc_shapefile,
  button_label = "Download hcmc shapefiles",
  output_name = "hcmc_shapefiles",
  output_extension = ".rds",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save"
)
```

### Using data

`hcmc_shapefile$merge_poly_fn()` can be used to quickly merge districts or communes

***Example:*** Generate district map during 2021 - 2023, with Thu Duc city

```{r warning=FALSE, message=FALSE}
thuduc_city <- hcmc_shapefile$merge_poly_fn(
  hcmc_shapefile$district_24,
  # specify merging D2, D9, Thu Duc into Thu Duc here
  merge_map = list(
    "Thu Duc city" = c("District 2", "District 9", "Thu Duc")
  ),
  colname = "varname_2" # merging by variable varname_2 (i.e., district lvl)
)

ggplot(thuduc_city) +
  geom_sf(aes(fill = varname_2))
```

***Example:*** Generate district map before 2003, without Tan Phu, Binh Tan

```{r warning=FALSE, message=FALSE}
pre_2003 <- hcmc_shapefile$merge_poly_fn(
  hcmc_shapefile$district_24,
  # generate data before the split 2003
  merge_map = list(
    "Tan Binh" = c("Tan Phu", "Tan Binh"),
    "Binh Chanh" = c("Binh Tan", "Binh Chanh")
  ),
  colname = "varname_2" # merging by variable varname_2 (i.e., district lvl)
)

ggplot(pre_2003) +
  geom_sf(aes(fill = varname_2))
```

## Plots

Plot changes in HCM city (at admin lvl 2)

```{r include=FALSE, eval=FALSE}
#| code-fold: true
#| code-summary: "Generate animation"
library(gganimate)

cropvector_postreform <- c(106, 107.8, 10.2, 12)

hcm_sf_timeline <- bind_rows(
  pre_2003 %>% mutate(period = "2000 - 2003"),
  hcmc_shapefile$district_24 %>% mutate(period = "2003 - 2021"),
  thuduc_city %>% mutate(period = "2021 - 2025"),
  hcmc_shapefile$commune_168 %>%
    mutate(period = "2025 - present") %>%
    st_crop(
      xmin = cropvector_postreform[1],
      xmax = cropvector_postreform[2],
      ymin = cropvector_postreform[3],
      ymax = cropvector_postreform[4]
    )
)

animation <- ggplot(hcm_sf_timeline) +
  geom_sf(aes(fill = name_2)) +
  transition_states(period, transition_length = 2, state_length = 1) +
  labs(title = "HCMC Administrative Lvl. 2 Boundaries — {closest_state}") +
  guides(fill = "none") +
  theme_minimal()

render <- gganimate::animate(
  animation,
  fps = 10,
  duration = 8,
  res = 200,
  width = 1100,
  height = 900,
  renderer = av_renderer("outputs/hcmc_lvl2_change.mp4")
)
```

```{r warning=FALSE, message=FALSE}
#| code-fold: true
#| code-summary: "Visualize changes"
cropvector_postreform <- c(106, 107.8, 10.2, 12)

walk2(
  list("2000 - 2003", "2003 - 2021", "2021 - 2025", "2025 - present"),
  list(
    pre_2003,
    hcmc_shapefile$district_24,
    thuduc_city,
    hcmc_shapefile$commune_168 %>%
      st_crop(
        xmin = cropvector_postreform[1],
        xmax = cropvector_postreform[2],
        ymin = cropvector_postreform[3],
        ymax = cropvector_postreform[4]
      )
  ),
  \(period, shape) {
    plt <- ggplot(shape) +
      geom_sf(aes(fill = varname_2)) +
      labs(title = paste0("HCMC Administrative Lvl. 2 Boundaries ", period)) +
      guides(fill = "none") +
      theme_minimal()

    print(plt)
  }
)
```