---
title: "Changes in Ho Chi Minh city map"
---

## Summary

Changes in administrative levels in HCM city from 2000 - 2026

-   **2003** - 2 new districts and reorganize communes ([source](https://vbpl.vn/TW/Pages/vbpqen-toanvan.aspx?ItemID=8462))

    -   Tan Phu (split from Tan Binh)

    -   Binh Tan (split from Binh Chanh)

-   **2006** - Reorganize communes in 3 districts ([source](https://chinhphu.vn/default.aspx?pageid=27160&docid=17997))

    -   Adjust communes in 3 districts: Go Vap, District 12, Tan Binh

-   **2021** - Establish Thu Duc city and **more** commune adjustments ([source](https://www.quanlynhanuoc.vn/2020/12/31/nghi-quyet-so-1111-nq-ubtvqh14-ve-viec-sap-xep-don-vi-hanh-chinh-cap-huyen-cap-xa-va-thanh-lap-tp-thu-duc-thuoc-tp-hcm/#:~:text=C%E1%BB%A5%20th%E1%BB%83%2C%20th%C3%A0nh%20l%E1%BA%ADp%20TP,s%E1%BB%91%20h%C6%A1n%201%20tri%E1%BB%87u%20ng%C6%B0%E1%BB%9Di.))

    -   Thu Duc city merged from 3 districts: 2, 9 and Thu Duc

    -   Adjust communes under Thu Duc city

-   **2023** - Reorganize communes (again) ([source](https://luatvietnam.vn/tin-van-ban-moi/sap-xep-dvhc-cap-xa-10-quan-cua-tp-hcm-giai-doan-2023-2025-186-100018-article.html))

    -   Adjust communes in several districts: 3,4,5,6,8,10, 11,Phu Nhuan, Binh Thanh, Go Vap

-   **2025** - Expand city and remove district level ([source](https://thuvienphapluat.vn/phap-luat/ho-tro-phap-luat/tra-cuu-168-phuong-xa-tphcm-chinh-thuc-sau-sap-nhap-nam-2025-day-du-chi-tiet-danh-sach-toan-bo-phuo-570655-223893.html))

    -   Merge Binh Duong and Vung Tau to Ho Chi Minh city

    -   Remove districts level, merge existing communes into 168 communes

Overview

-   **2000 - 2003:** 22 districts, 317 communes

-   **2003 - 2021:** 24 districts, 322 communes

-   **2021 - 2023:** 22 districts, 312 communes

-   **2023 - 2025:** 22 districts, 273 communes

-   **2025 - present (April, 2026):** 168 communes

## Data

Not all changes are reflected on open sourced shapefiles. The data are separated into 3 periods:

-   GADM 4.1 (24 districts, 322 communes)

    -   Manual merge into 22 districts, 322 communes

-   GIS VN (168 communes)

```{r}
# Load some dependencies
library(tidyverse)
library(sf)
library(janitor)
```

```{r}
#| collapse: true
#| summary: "Generate data"

# Roughly HCMC spatial extent
cropvector <- c(106.2, 107.2, 10.2, 11.3)
# hcmc_extent <- ext(cropvector)

district_24 <- read_sf("data/raw/before_reforms/gadm41_VNM_shp/gadm41_VNM_2.shp",
                       options = "ENCODING=UTF-8") %>% 
  clean_names() %>% 
  st_crop(
    xmin = cropvector[1],
    xmax = cropvector[2],
    ymin = cropvector[3],
    ymax = cropvector[4]
  ) %>%
  filter(gid_1 == "VNM.25_1")

district_24

# The 22 districts map
# TODO: manual merge

# The 168 communes map
commune_168 <- read_sf("data/raw/after_2025_reforms/Việt Nam (phường xã) - 34/",
                       options = "ENCODING=UTF-8") %>% 
  filter(ten_tinh == "TP. Hồ Chí Minh") 

commune_168 %>% 
  rename(
    name_1 = ten_tinh,
    name_2 = ten_xa,
    type_2 = loai
  )
```

Data format

```{r}

```

```{r}
# Download data
```

## Visualize

Plot changes in HCM (at admin lvl 2)

Plot changes in HCM (at admin lvl 3)
